\documentclass[twocolumn]{article}

\title{CS141 -- Intermediate Algorithms and Data Structures\\Assignment 2 -- All
Pairs Shortest Path}
\author{[Your Name Here]}
\date{}

\begin{document}
\maketitle

\section*{Abstract}
\textbf{\small}

\section{Introduction}
\begin{itemize}
    \item What is the problem that you are solving?
    \item What methods are you going to use to solve the problem?
    \item Why are these good methods to use?
    \item Why are you going to be using both of them?
\end{itemize}

\section{Bellman-Ford}
\begin{itemize}
    \item What is the Bellman-Ford algorithm?
    \item Why are you using it?
    \item How did you adapt it to work for all-pairs as opposed to single
    source?
    \item What is the run-time of the algorithm before and after your
    adaptation?
\end{itemize}

\section{Floyd-Warshall}
\begin{itemize}
    \item What is the Floyd-Warshall algorithm?
    \item Why are you using it?
    \item How is it better than the Bellman-Ford algorithm?
    \item What is the run-time of the algorithm?
\end{itemize}

\section{Results}
\begin{itemize}
    \item Compare and contrast the two algorithms? What makes one more suited
    for this problem?
    \item What are their theoretical run-times (from the previous sections) and
    how do they compare?
    \item What are the actual run-times that you computed? Which method is
    better? Why?
\end{itemize}

% Fill in the following table
\begin{table}
    \begin{tabular}{|c|c|c|c|c|}
        \hline
        &\multicolumn{2}{|c|}{Bellman-Ford}&\multicolumn{2}{|c|}{Floyd-Warshall}\\
        \cline{2-5}
        Benchmarks&$O(.)$&Actual&$O(.)$&Actual\\
        \hline
        input1.txt&      &      &      &      \\
        \hline
    \end{tabular}
\end{table}

\section{Conclusions}
\begin{itemize}
    \item What did you find difficult about the assignment?
    \item What did you learn?
    \item What is one real-world problem that you think each of these problems
    would be good at solving?
\end{itemize}

\end{document}
